---
title: "Exercise06"
author: "Ken Suzuki"
date: "2023-12-10"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Conditions & Background:   

This exercise will use the dataset 'disgusting_scale.csv', available on eClass. The main outcome variables are **scores on the Disgust Scale Revised**. This scale contains three factors:

1.  **The 'Core Disgust', a mechanism which elevates awareness about disease.**

2.  **The 'Animal Reminder', a mechanism which elevates awareness to human animalistic nature.**

3.  **The 'ContaminationBased Disgust', which contains items related to dangers of contamination. There is also a 'General Disgust Score' across all items.**

***Use a = .05 for both questions.***

### Tasks

#### Conduct a general linear model to explore the effects of age (Age) and education (Educ) on the general disgust score (Mean_general_ds). Note: use the categorical version of education (Educ) for this question. 

```{r}
d <- read.csv("~/Desktop/P4330/P4330 R code/Exercise06/Multiplicity Control/disgust_scale.csv") #disgust_scale.csv
names(d)
head(d)
library(emmeans)

m <- lm(Mean_general_ds ~ Educ + Age, data = d)
summary(m)

```

#### Conduct all pairwise comparisons for education using each of the following methods: a) No multiplicity control; b) Bonferroni familywise error control; c) Benjamini- Hochberg false discovery rate control. Summarize which effects are statistically significant with each method.

```{r}
mns <- emmeans(m, "Educ")
pairs(mns, adjust="none")
```

**Bonferroni**

```{r}
pairs(mns, adjust="bonferroni")
```

**f**

```{r}
pairs(mns, adjust="fdr")
```

#### Conduct a general linear model to explore the effects age (Age), gender (Gender), and education (Education) on each of the factors of the Disgust Scale (Mean_Animal_reminder, Mean_core, Mean_Contamination). Note: use the continuous version of education (Education) for this question. 

##### 1. The 'Core Disgust' - a mechanism which elevates awareness about disease. 

```{r}
# Build each model 

m2 <- lm(Mean_Animal_reminder ~ Age + Gender + Education,
         data = d)
summary(m2)
```

##### 2. The 'Animal Reminder'- a mechanism which elevates awareness to human animalistic nature. 

```{r}
# Build each model 
m3 <- lm(Mean_Contamination ~ Age + Gender + Education,
         data = d)
summary(m3)
```

##### 3. The 'ContaminationBased Disgust'- which contains items related to dangers of contamination. There is also a 'General Disgust Score' across all items.

```{r}
# Build each model 
m4 <- lm(Mean_core ~ Age + Gender + Education,
   data = d)
summary(m4)
```

#### Treat the full collection of hypotheses as a single family (i.e., each of the three predictors across each of the three outcome variables - 9 total hypothesis tests). 

```{r}
pvals<-c(summary(m2)$coefficients[2:4,4],
         summary(m3)$coefficients[2:4,4],
         summary(m4)$coefficients[2:4,4])
pvals
names(pvals) <- c("age_ar", "gender_ar", "educ_ar",
                  "age_con", "gender_con", "educ_con",
                  "age_cor", "gender_cor", "educ_cor")
```

#### Assess the statistical significance of each hypothesis using each of the following methods: 

##### a) No multiplicity control; 

```{r}
p.adjust(pvals, method = "none")
```

##### b) Bonferroni familywise error control; 

```{r}
p.adjust(pvals, method = "bonferroni")
```

##### c) Holm familywise error control; 

```{r}
p.adjust(pvals, method = "holm")
```

##### d) BenjaminiHochberg false discovery rate control. Summarize which effects are statistically significant with each method.

```{r}
p.adjust(pvals, method = "fdr")
```
